\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer} % Job title
    {Securiport LLC} % Organization
    {Washington, DC} % Location
    {December 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Driving the introduction of automated unit testing practices into the existing code base. Aiming for 80\% code coverage or higher on new code.}
        \item {Design and implementation of new components. Maintenance and bug fixes on existing components.}
        \item {Identified and eliminated performance issue in core system which caused the entire system to slow down during high load times.}
        \item {Working with service oriented system based on monolith WCF service and some RESTful .Net Core services and MSSQL Server, NUnit.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer (Remote)} % Job title
    {Alpine Metal Tech North America Inc.} % Organization
    {Vienna, VA} % Location
    {May 2019 - November 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {High degree of self organization due to 100\% remote work.}
        \item {On-site customer support.}
        \item {Continuation of responsibilities at Alpine Metal Tech GmbH.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer} % Job title
    {Alpine Metal Tech GmbH} % Organization
    {Regau, Austria} % Location
    {August 2018 - April 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, development, maintain, and support applications written in C\# used in the automotive industry to monitor the production and quality of alloy rims.}
        \item {Work collaboratively with clients to provide customer specific solutions which meet their needs.}
        \item {Desktop system based on .Net Framework, WinForms UI, PostgreSql server, communication with PLC to control mechanical movements.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer} % Job title
    {IGT Geotechnik und Tunnelbau GmbH} % Organization
    {Salzburg, Austria} % Location
    {January 2018 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and develop new features for a specialized Windows application used by geotechnical engineers to monitor earth movement.}
        \item {Desktop application in .Net Framework, DevExpress WinForms, MSSQL Server.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer/Master's Thesis} % Job title
    {Infineon Austria AG} % Organization
    {Graz, Austria} % Location
    {November 2016 - September 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research, design, and implementation of a “free space finding algorithm” based on point cloud data on a mobile phone.}
        \item {Google Tango enabled Android phone, Android NDK, OpenCL, PointCloudLibrary ported to Android, Java.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer (Intern)} % Job title
    {Infineon Austria AG} % Organization
    {Graz, Austria} % Location
    {July 2015 - October 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improving, maintaining, and introducing automated testing into existing applications.}
        \item {Major redesign of an application, moving from file based data store to SQL to allow better control over concurrency issues.}
        \item {Java, XML, Oracle Server, JUnit.}
      \end{cvitems}
    }
\end{cventries}
